---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# datagovgR

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

<!-- badges: end -->

R wrapper package for the [data.gov.gr](https://www.data.gov.gr) API.

The goal of datagovgR is to enable R users, data analysts, academics and students to work with the Greek open governmental data programmatically. By default, the package returns queries from the v1 API on <https://data.gov.gr/api/v1/>. *Unfortunately, no official documentation has come to my attention for this API.*

The following endpoints are currently available through the package:

-   **"mdg_emvolio"** Covid-19 Vaccination Statistics

## Installation

You can install the development version of datagovgR using [devtools](https://github.com/r-lib/devtools "Devtools package") like so:

``` r
# install.packages("devtools")
devtools::install_github(hypnicjerk91/datagovgR)
```

## What else do I need?

You will need an access token to retrieve records from data.gov.gr. You may request for your API token on <https://www.data.gov.gr/token>. After your request, check your email regularly for your data.gov.gr API token.

## Setting up

#### Telling datagovgR about your API token

You have to set your token once for all your API calls to use with the package's corresponding function.

To set:

``` r
set_token("token abcd12344321")
```

To retrieve your token (if needed):

``` r
get_token()
```

## 'GET'ting data

This is a basic example which shows you how to query the API. You will have to set the endpoint/dataset you are going to call, start_date (optional) and end_date (optional).

```{r example, eval=FALSE, include=TRUE}
install_github("hypnicjerk91/datagovgR")
library(datagovgR)
data <- gov_query("mdg_emvolio","2022-07-04","2022-07-11")
## basic example code using the Covid-19 Vaccination dataset
```

```{r vaccinations, eval=FALSE, include=TRUE}
summary(data)
```

## Related projects

-   [go-data-gov-gr-sdk](https://github.com/ppapapetrou76/go-data-gov-gr-sdk) Go client to access the data.gov.gr API.

-   [pydatagovgr](https://github.com/ilias-ant/pydatagovgr) Python client to access the data.gov.gr API.

## License

Distributed under the MIT License.

## Acknowledgements

All rights are reserved by the official <https://data.gov.gr> site, its developers, its maintainers and the Hellenic Government.
